\SW: I. Crowd-sourcing the Discovery of Gravitational Lenses

### 2015-07-23 doc/sw-system.tex
Added Matthias to acknowledgments

We thank Stuart Lynn, Kelly Borden, Laura Whyte, Brooke Simmons, David Hogg,
Daniel Foreman-Mackey, Thomas Jennings, Layne  Wright, Cecile Faure, Jonathan
Coles, Stuart Lowe and Jean-Paul Kneib for many useful conversations about
citizen science and gravitational lens detection, and to the Dark Energy Survey
and Pan-STARRS strong lensing science teams for their suggestions and
encouragement.

>>>>

We thank Matthias Tecza, Stuart Lynn, Kelly Borden, Laura Whyte, Brooke Simmons, David Hogg,
Daniel Foreman-Mackey, Thomas Jennings, Layne  Wright, Cecile Faure, Jonathan
Coles, Stuart Lowe and Jean-Paul Kneib for many useful conversations about
citizen science and gravitational lens detection, and to the Dark Energy Survey
and Pan-STARRS strong lensing science teams for their suggestions and
encouragement.
